Towards practical dynamic induction control of wind farms: analysis of optimally controlled wind-farm boundary layers and sinusoidal induction control of first-row turbines

### 2018-05-17 revision/reply_to_revs_2.tex
Trivial changes to REv2

\textbf{Response: } WM - Ik vind de commentaar van de reviewer hier vrij verwarrend. Weet niet exact wat hij hier bedoelt. Hopelijk is onderstaand antwoord voldoende.

%We thank the reviewer for this comment. We believe that the statement referred to by the reviewer still holds, i.e.
%
%``An interesting observation from this figure is that , for any row $i$ except the last one, the power potential as observed in case C3t5 is almost fully recovered by
%only applying the optimal controls up to row $i-1$''. 
%
%This is a simple observation that stems directly from the data in the figure. Unless we misinterpret the point of the reviewer, we do not agree that a curtailment strategy would invalidate this statement. If, let's say, a curtailment strategy would have been incorporated into the control law for row $i$ (i.e. to the benefit of row $i+1$), the application of the control R1-R$_{i-1}$ would yield even greater power gains in row $i$ than when applying controls R1-R$_i$, so the statement would still hold. 
%
%However, we do agree that statements and conclusions made throughout section 3 are specific to the current case and should therefore be interpreted with care. We have updated the manuscript to be more explicit that results are not overall conclusions for wind-farm control in general, but should be interpreted as observations of the current optimal control case. This has been done at the beginning of Section 3, prior to the elaboration of analyses and experiments as follows (l XX p XX):
%
%`` 
%... to uncover some of the characteristics of these control signals. \textbf{Note that the conclusions drawn within this paragraph should be interpreted as observations of the current C3t5 optimal control cases, given specific wind-farm layout and flow conditions, and hence cannot just be generalized for any wind-farm control in general.}
%''
%
%We hope that the updates to the manuscript encompass the concerns expressed by the reviewer.

We thank the reviewer for this comment. We agree that statements and conclusions made throughout section 3 are specific to the current case and should therefore be interpreted with care. However, possible curtailment is not the only reason why certain statements in this section could be invalidated, e.g. possible phase-locked correlated control actions between turbines (which were found not to be present in the current case) would invalidate the same statement as referred to by the reviewer.

We have updated the manuscript to be more explicit in the sense that results are not overall conclusions for wind-farm control in general, but should be interpreted as observations of the current optimal control case. This has been done at the beginning of Section 3, prior to the elaboration of analyses and experiments as follows (l XX p XX):

@@

However, we do believe that the sinusoidal thrust control strategy is something that can be generalized to other wind-farm setups (as evidenced by Section 4.2.2). We hope that the updates to the manuscript encompass the concerns expressed by the reviewer.

@@

``
whereas the time synchronization of control actions to specific flow events is 10 eliminated. Similar to the first case, this is done in 2 random ways, \textbf{and the limited correlation between velocity fluctuations in different time windows was quantified at 0.07}. Figure 11b illustrates the row-averaged power for these...
cases.
''

>>>>

\textbf{Response: } We find it difficult to follow the argument formulated by the reviewer here. However, we agree in general that statements and conclusions made throughout section 3 are specific to the current case and should therefore be interpreted with care.

We have updated the manuscript to be more explicit in the sense that results are not overall conclusions for wind-farm control in general, but should be interpreted as observations of the current optimal control case. See the beginning of Section 3 (l XX p XX):

@@

@@

``
whereas the time synchronization of control actions to specific flow events is eliminated. Similar to the first case, this is done in 2 random ways, \textbf{and the limited correlation between velocity fluctuations in different time windows was quantified at 0.07}. Figure 11b illustrates the row-averaged power for these...
cases.
''
